### 2023-04-16 main.tex
s

We will exploit   the duality and th underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. 

>>>>

We will exploit the duality and the underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. 
